As we discussed in the previous sections, the first step that we need to implement in order to estimate the 3D human pose from a video is to estimate the 2D human pose \cite{Exploiting temporal information for 3D pose estimation,3D Human Pose Estimation = 2D Pose Estimation + Matching}. Therefore, we have to find a deep neural network that can do such a task. There are two different ways that we could follow here. \\

On the one hand, we could build a deep neural network from scratch, which is definitely not an easy task to do. This is a very time-consuming procedure since someone must find a promising architecture for the model, and find an enormous Dataset that most of the time needs editing and is not free. However, the training of the deep neural network is the major problem, especially in our case. The goal of the training is to find the ideal parameters that will minimize the loss function of the network. An epoch is one complete pass of the training dataset through the algorithm, and the network has to run many epochs during training to calibrate its weights and bias. Neural network training is a very slow process that depends on the machine that the DNN runs as well as the Dataset size and the training parameters (batch size, early stop, etc.). In our case, the Dataset size that relatives work use contains videos that are many Terabytes of data, which is an enormous amount. Therefore, the training even though a single epoch needs many hours in a state-of-the-art machine learning graphic card, means that in our system would too much time (even days). So, even though we would build our network, the drawbacks are too many, leaving this option as a last resort.\\

On the other hand, we could search to find a pre-trained deep neural network that does our job. Luckily for us, some pre-trained models are trained to estimate exactly what we needed. These models were constructed by many researchers (professors, Ph.D. students, etc.). They had a budget, that helped them find a great Dataset, as well as the latest technology Hardware to train the DNN. The models that we are discussing are  AlphaPose and OpenPose. All of them can estimate the 2D human pose from an image or a sequence of images with great accuracy. These models are trained to do much more than we need in this thesis. They can estimate in Real-time the 2D human pose from a Web-Cam and they can detect and estimate the 2D human pose from multiple people at once. We only need to estimate the pose from a single person from a video. By reading the documentation of these models, we can achieve that.\\

The most important advantage of using a pre-trained model, that satisfies our needs, is that we can avoid all the drawbacks that we discussed in the case that we would create our model. In our case, these models are very powerful, they have great accuracy, so they do not even need further training.