\begin{thebibliography}{9}

\bibitem{Efficient Content-Based Retrieval of Motion Capture Data}
M{\"u}ller, Meinard and R{\"o}der, Tido and Clausen, Michael ACM SIGGRAPH 2005 Papers 677--685\\

\bibitem{Exploiting temporal information for 3D pose estimation}
Rayat Imtiaz Hossain, Mir, and James J. Little. "Exploiting temporal information for 3D pose estimation." arXiv e-prints (2017): arXiv-1711.\\

\bibitem{3D Human Pose Estimation from Deep Multi-View 2D Pose}
Schwarcz, Steven, and Thomas Pollard. "3d human pose estimation from deep multi-view 2d pose." 2018 24th International Conference on Pattern Recognition (ICPR). IEEE, 2018.\\

\bibitem{3D Human Pose Estimation Using Convolutional Neural Networks with 2D Pose Information}
Park, Sungheon, Jihye Hwang, and Nojun Kwak. "3d human pose estimation using convolutional neural networks with 2d pose information." European Conference on Computer Vision. Springer, Cham, 2016.\\

\bibitem{Review on Motion Capture Technology}
Rahul, M. "Review on motion capture technology." Global Journal of Computer Science and Technology (2018).\\

\bibitem{Optical Motion Capture: Theory and Implementation}
Guerra-Filho, Gutemberg. "Optical Motion Capture: Theory and Implementation." RITA 12.2 (2005): 61-90.\\

\bibitem{Kalman Filtering for Sensor Fusionin a Human Tracking System}
Corrales Ramón, Juan Antonio, Francisco A. Candelas-Herías, and Fernando Torres. Kalman filtering for sensor fusion in a human tracking system. Intech, 2010.\\

\bibitem{MOTION CAPTURE TO BUILD A FOUNDATION FOR A COMPUTER-CONTROLLED INSTRUMENT BY STUDY OF CLASSICAL GUITAR PERFORMANCE}
 Norton, Jonathan Carey. Motion capture to build a foundation for a computer-controlled instrument by study of classical guitar performance. Stanford University, 2008.\\
 
\bibitem{Deep Learning}
https://www.deeplearningbook.org/\\

\bibitem{ANIMGAN: A SPATIOTEMPORALLY-CONDITIONED GENERATIVE ADVERSARIAL NETWORK FOR CHARACTER ANIMATION}
Mirzaei, Maryam Sadat, et al. "Animgan: A spatiotemporally-conditioned generative adversarial network for character animation." 2020 IEEE International Conference on Image Processing (ICIP). IEEE, 2020.\\

\bibitem{3D Human Pose Estimation = 2D Pose Estimation + Matching}
Chen, Ching-Hang, and Deva Ramanan. "3d human pose estimation= 2d pose estimation+ matching." Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2017.\\

\bibitem{The importance of the loss function in option valuation}
Christoffersen, Peter, and Kris Jacobs. "The importance of the loss function in option valuation." Journal of Financial Economics 72.2 (2004): 291-318.\\

\bibitem{Human3.6M}
Ionescu, Catalin, et al. "Human3. 6m: Large scale datasets and predictive methods for 3d human sensing in natural environments." IEEE transactions on pattern analysis and machine intelligence 36.7 (2013): 1325-1339.\\

\bibitem{OpenPose}
Cao, Zhe, et al. "Realtime multi-person 2d pose estimation using part affinity fields." Proceedings of the IEEE conference on computer vision and pattern recognition. 2017.\\

\bibitem{HrNet}
Sun, Ke, et al. "Deep high-resolution representation learning for human pose estimation." Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2019.\\

\bibitem{AlphaPose}
Fang, Hao-Shu, et al. "Rmpe: Regional multi-person pose estimation." Proceedings of the IEEE international conference on computer vision. 2017.\\

\bibitem{ANIMGAN}
Mirzaei, Maryam Sadat, et al. "Animgan: A spatiotemporally-conditioned generative adversarial network for character animation." 2020 IEEE International Conference on Image Processing (ICIP). IEEE, 2020.\\

\bibitem{Human Action Generation with Generative
Adversarial Networks}
Kiasari, Mohammad Ahangar, Dennis Singh Moirangthem, and Minho Lee. "Human action generation with generative adversarial networks." arXiv preprint arXiv:1805.10416 (2018).\\

\bibitem{SPPE}
Zhang, Feng, Xiatian Zhu, and Chen Wang. "Single Person Pose Estimation: A Survey." arXiv preprint arXiv:2109.10056 (2021).\\

\bibitem{YOLO-Pose}
Maji, Debapriya, et al. "YOLO-Pose: Enhancing YOLO for Multi Person Pose Estimation Using Object Keypoint Similarity Loss." arXiv preprint arXiv:2204.06806 (2022).\\

\bibitem{YOLOv3}
Redmon J, Farhadi A, "YOLOv3: an Incremental Improvement," https://arxiv.org/
abs/1804.02767, 2018.

\bibitem{HourGlass}
Newell, Alejandro, Kaiyu Yang, and Jia Deng. "Stacked hourglass networks for human pose estimation." European conference on computer vision. Springer, Cham, 2016.

\bibitem{Attention Mechanism Exploits Temporal Contexts: Real-time 3D Human Pose Reconstruction}
Liu, Ruixu, et al. "Attention mechanism exploits temporal contexts: Real-time 3d human pose reconstruction." Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2020.\\

\bibitem{3D human pose estimation in video with temporal convolutions and
semi-supervised training}
Pavllo, Dario, et al. "3d human pose estimation in video with temporal convolutions and semi-supervised training." Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2019.\\

\bibitem{Mean Filtering}
Chandrinos, Aristeidis. "The Challenge of Predicting OAG Progression from the Initial Visual Field Test." Signal 4: 6.\\

\bibitem{Gaussian Filtering}
Ramamurthy, Arjun. "An All Digital Implementation of Constant Envelope: Bandwidth Efficient GMSK Modem using Advanced Digital Signal Processing Techniques." Wireless personal communications 52.1 (2010): 133-146.\\

\bibitem{Butterworth Filtering}
Cuadrado, Javier, Florian Michaud, Urbano Lugrís, and Manuel Pérez Soto. "Using accelerometer data to tune the parameters of an extended kalman filter for optical motion capture: Preliminary application to gait analysis." Sensors 21, no. 2 (2021): 427.\\

\bibitem{Tkinter 1}
Lundh, Fredrik. "An introduction to tkinter." URL: www. pythonware. com/library/tkinter/introduction/index. htm (1999).\\

\bibitem{Tkinter 2}
Grayson, John E. Python and Tkinter programming. Manning Publications Co. Greenwich, 2000.\\



\end{thebibliography}

